Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-07-03 MCQMC2022ChallengesQMCSoftwareArticle_revision_1.tex
changes before 7/3

\SCComment{In QMCPy, we recognize the crucial role of non-code contributors to the project~\cite{K23}. Besides coding, we also need documentation, data visualization,  testing, user interface or experience design, web content development, community management, and release management. These non-code contributions help make the project more  accessible. Non-coding roles offer opportunities for individuals with less coding experiences to develop technical and non-technical skills over time.  Additionally, the emergence of no-code or low-code analytical software such as RapidMiner, KNIME, Orange, SAS Studio, or SAS Viya offer a chance for individuals who are less experienced with complex coding to learn and contribute in a more user-friendly environment.  We need and welcome non-code contributors to work alongside code contributors, enhancing the overall health of the project and the diversity of the community. }

>>>>

\SCComment{In QMCPy, we recognize the crucial role of non-code contributors to the project~\cite{K23}. Besides coding, we also need documentation, data visualization,  testing, user interface or experience design, web content development, community management, and release management. These non-code contributions help make the project more  accessible. Non-coding roles offer opportunities for individuals with less coding experiences to develop technical and non-technical skills over time.  Additionally, the emergence of no-code or low-code analytical software such as RapidMiner, KNIME, Orange, SAS Studio, or SAS Viya enable individuals less experienced with complex coding to learn and contribute in a user-friendly environment.  We need and welcome non-code contributors to work alongside code contributors for QMCPy, enhancing the overall health of the project and the diversity of the community. }
